Nail: A practical interface generator for data formats

### 2014-08-21 paper/osdi14/intro.tex
Intro

A promising approach to avoid such vulnerabilities is to specify
a precise grammar for the input data format, and to use a parser
generator, such as {\tt lex} and {\tt yacc}, to synthesize the input
processing code.  Developers that use a parser generator do not need
to write error-prone input processing code on their own, and as long
as the parser generator is bug-free, the application will be safe from
input processing vulnerabilities.

>>>>

Typically, input parsers, particularly for binary formats, are often
written by hand. Not only is such code plagued by the bugs mentioned above, but
two separate hand-written implementations of the same protocol might disagree on
the meaning of a particular input, which can lead to security
vulnerabilities~\cite{saurik-masterkey}.

A promising approach to avoid these problems is to specify
a precise grammar for the input data format, and to use a parser
generator, such as {\tt lex} and {\tt yacc}, to synthesize the input
processing code.  Developers that use a parser generator do not need
to write error-prone input processing code on their own, and as long
as the parser generator is bug-free, the application will be safe from
input processing vulnerabilities. Grammars can be re-used between
applications, further reducing effort and eliminating ambiguities.
